---
title: "API - plantnet"
output: html_document
---

devtools::install_github(repo = 'BiologicalRecordsCentre/plantnet')

```{r setup, include=FALSE}
library(plantnet)
library(dplyr)
library(httr)
```

#HTTP POST remote images
https://my.plantnet.org/account/doc
* Must use POST for local images upload, where GET for online urls
##Identification service params:

service: https://my-api.plantnet.org/v2/identify/all
api-key: api-key=2a10ugoftmL4lZtukHdV8DvDWu
image_1: images=/data/media/image_1.jpeg
image_2: images=/data/media/image_2.jpeg
organ_1: organs=flower
organ_2: organs=leaf

```{r}
# Get your key from https://my.plantnet.org/
key <- as.character(read.table("plantnetkey.txt"))   # Personal key, please do not use without permission [limited to 50 uses per day]

getSpecies <- function(key, imageURL) {
  
  # Currently getSpecies only accepts url as the PlantNet API requires image access
  # Need to allow image submission to API or host image to send url
  classifications_check <- identify(key = key, imageURL = imageURL)
  
  if(classifications_check[1,1]$score > 10) {
    classification <- unlist(classifications_check[1,c(2,3)])
  }
  else {
    print("Insufficent accuracy. Cannot identify name. Please use other images")
  }
  return(classification)
}

```

```{r}
# Get the URL for your image
imageURL <- 'https://cdn.pixabay.com/photo/2020/05/09/17/04/thistle-5150476_960_720.jpg'
species1 <- getSpecies(key, imageURL)

imagepath <- upload_file("/home/agar2/Documents/Local-species-catalogue/Pictures/IMG_20200729_163347.jpg")
```

```{r}
#It's Alive!!
url <- paste("https://my-api.plantnet.org/v2/identify/all?api-key=", key, sep = "")
plantnetPOST <- httr::POST(url = url,
                           add_headers(`Content-Type`="multipart/form-data"),
                                body = list(
                                  images = imagepath,
                                  organs = "flower"
                                  ),
                              encode = "multipart"
                           )
content(plantnetPOST)

```
Per Postman building via desktop app connection:
curl --location --request POST 'https://my-api.plantnet.org/v2/identify/all?api-key=2a10ugoftmL4lZtukHdV8DvDWu' \
--form 'images=@vfAqlnPvw/IMG_20200729_163347.jpg' \
--form 'organs=flower'

param: api-key
body: images{@file}, organs

HTTP Status Code	Reason	Response Model	Headers
400	Bad Request
401	Unauthorized
404	Species Not Found
413	Payload Too Large
414	URI Too Long
415	Unsupported Media Type
429	Too Many Requests
500	Internal Server Error