---
title: "GPS_map"
output: html_document
---

Tasks:
- Check osmdata package requirement, after settling on Google API method via ggmap package
- See osmdata::available_features() if maps require additional identity markers

system("apt install libudunits2-dev") # sf package

Ref1: https://cran.r-project.org/web/packages/osmdata/vignettes/osmdata.html
Ref2: https://dominicroye.github.io/en/2018/accessing-openstreetmap-data-with-r/
```{r}
#install the osmdata, sf, tidyverse and ggmap package
if(!require("osmdata")) install.packages("osmdata")  
if(!require("sf")) install.packages("sf")
# remove.packages(ggmap)   # Required when CRAN version previously installed
if(!require("ggmap")) devtools::install_github("dkahle/ggmap")


#Enter Google Maps enabled API key (used Static Maps API)
##To enable, 
## 1) must create Google Cloud Platform account, 
## 2) create a project, then 
## 3) enable the Maps API key via APIs & Services > Credentials > + Create Credentials > API key 
register_google(key = rstudioapi::askForPassword("ENTER GOOGLE API KEY HERE"), 
                account_type = "standard", 
                write = T)  # write = T save the API key to environment so it doesn't have to be declared more than once

```

# Get File + GPS data 
GPS_extract.Rmd [to be done in level 2 script]
pic1.gps

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#load packages
library(dplyr)
library(sf)
library(ggmap)

# Not used
#library(osmdata)
#library(OpenStreetMap)   
```
> Based on 1-10 observations, map boundaries require minimum area for plotting

```{r}
#building the query
q <- getbb("Toronto") %>%
      opq() %>%
       add_osm_feature("amenity", "cinema")
cinema <- osmdata_sf(q)
#our background map
mad_map <- get_map(getbb("Toronto"), maptype = "toner-background")
#final map
ggmap(mad_map)+
  geom_sf(data = cinema$osm_points,
          inherit.aes = FALSE,
          colour = "#238443",
          fill = "#004529",
          alpha = .5,
          size = 4,
          shape = 21)+
  labs(x = "", y = "")
```

> Latitude, Longitude (order)

Note: 
- If copying coordinates from Google maps, the get_map function requires longitude first, as opposed to the former providing lattitude first

```{r}
# Get getBB box
bb <- make_bbox(pic1.gps$GPSLongitude, pic1.gps$GPSLatitude)

# Map tile
map <- ggmap(get_map(location = c(pic1.gps$GPSLongitude, pic1.gps$GPSLatitude), zoom = 21, maptype = "satellite"))
```


> Ref3: https://www.nceas.ucsb.edu/sites/default/files/2020-04/ggmapCheatsheet.pdf


```{r "GPS data"}
# Map with gps coordinates
gps1 <- data.frame(species = "arabidopsis", lon = -79.26887718018865, lat = 44.2486202976625)   # randomly taken from Google maps
gps2 <- data.frame(species = "arabidopsis", lon = -79.26818923287712, lat = 44.2487061833985)   # randomly taken from Google maps
gps3 <- data.frame(species = "dinosaur", lon = -79.26616416507017, lat = 44.24929218118515)   # randomly taken from Google maps

gps <- rbind(gps1, gps2, gps3)
```

```{r "Mapping"}
# Note: make_bbox works as expected when ggmap packaged sourced via Github, not via Cran version. Remove package and install git version.
map <- get_map(location = make_bbox(lon = gps$lon, 
                                    lat = gps$lat),
               zoom = 17,                                 # Potential: Shinyapp variable
               maptype = "satellite", 
               source = "google")

ggmap(map) + 
  geom_point(data = gps, 
              aes(colour = species),
              alpha = 1, 
              shape = 20,
              #color="red", 
              size = 3)

# Add geom_labels per observation


# Add plant image (low version) to coordinates [attempt Ref3, "4. Annotate figure"]
```


