---
title: "Image extract"
output: html_document
---

system("apt-get install exif")

> tools reference
http://paleolimbot.github.io/tutorial/rexiftool.html
https://exiftool.org/


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(exifr)
library(dplyr)
```

> Get from image
1) Geolocation
2) Timestamp

```{r}
# GPS coordinates and timestamp available

getImagedata <- function(location){

# Download and read online image
# download.file(url = location, "image")
# loc <- read_exif("image")

# Read online image  
  loc <- read_exif(location)
  loc <- loc %>% select(FileName, 
                        GPSTimeStamp,
                        GPSDOP,
                        GPSDateStamp,
                        GPSLatitude,
                        GPSLongitude
               )
# system("rm image")
  return(loc)
}

# pic1 <- read_exif("Pictures/IMG_20191207_215918.jpg")
# pic1.gps <- cbind("FileName"= pic1$FileName, pic1[1,startsWith(colnames(pic1),"GPS")])
# 
# # Ex of no GPS data
# pic2 <- read_exif("Pictures/20190615_184057.jpg")
# pic2.gps <- pic2[1,startsWith(colnames(pic2),c("FileName", "GPS"))]
```
Image flower = IMG_20200729_163347.jpg

```{r}
imageURL <- 'https://cdn.pixabay.com/photo/2020/05/09/17/04/thistle-5150476_960_720.jpg'
download.file(imageURL, "temp.jpg"); read_exif("temp.jpg")

imagedata <- getImagedata("Pictures/IMG_20200729_163347.jpg")

# Todo:
# Write TryCatch methods to distinguish images downloaded via links (ie. Google Photos, etc [must have open access downloadable conditions])
```

https://en.wikipedia.org/wiki/Dilution_of_precision_(navigation)
# DOP Value	Rating	Description
1	Ideal	Highest possible confidence level to be used for applications demanding the highest possible precision at all times.
1-2	Excellent	At this confidence level, positional measurements are considered accurate enough to meet all but the most sensitive applications.
2-5	Good	Represents a level that marks the minimum appropriate for making accurate decisions. Positional measurements could be used to make reliable in-route navigation suggestions to the user.
5-10	Moderate	Positional measurements could be used for calculations, but the fix quality could still be improved. A more open view of the sky is recommended.
10-20	Fair	Represents a low confidence level. Positional measurements should be discarded or used only to indicate a very rough estimate of the current location.
'>20'	Poor	At this level, measurements are inaccurate by as much as 300 meters with a 6-meter accurate device (50 DOP × 6 meters) and should be discarded.
