---
title: "L2-map species"
output: html_document
---

1. Image -> species name
  # https://my.plantnet.org/usage
  # https://github.com/BiologicalRecordsCentre/plantnet
2. species name -> gbif data
3. Image -> GPS data
4. Map image + name + GPS
  
Docs:
- To get locations with images, currently must manually enable via camera app > settings > location with photos or similar option
- Must use image sharable weblink (hosted via accessible server like Google Photos or OneDrive)

# Image GPS & timestamp extract [done]
GPS_extract.Rmd
```{r Data Input}
imagedata <- getImagedata(imageURL)
```
TODO
 - Create image uri (image_id), based on image.gps & image.time (consider ontology uri generation, additional input: Domain)
STORAGE
 - Postgres (lo) vs MongoDB (base64)

# Image recognition API via PlantNet [done]
API-plantnet.Rmd
plantnetkey.txt
```{r PlantNet Species Recognition API}
imageURL <- 'https://photos.app.goo.gl/srRoYVB7zH3uA6qs9'
species1 <- getSpecies(key, imageURL)
```
TODO
 - Multiple image submission for identification API

# Species data via GBIF API [incomp]
GBIF data.Rmd
```{r GBIF Data API}

```

# Map Image GPS [done]
GPS_map.Rmd
```{r OpenStreetMap}
map_plot
```
TODO
 - Observation image tile on map
 - Review GeoServer for hosting/interoperability of geodata

# Shiny time-series
```{r Shinyapp}

```


