---
title: "L2-map species"
output: html_document
---

1. Image -> species name
  # https://my.plantnet.org/usage
  # https://github.com/BiologicalRecordsCentre/plantnet
2. species name -> gbif data
3. Image -> GPS data
4. Map image + name + GPS
  
Docs:
- To get locations with images, currently must manually enable via camera app > settings > location with photos or similar option
- Must use image sharable weblink (hosted via accessible server like Google Photos or OneDrive)

# Outline
Outline.Rmd

# Image GPS & timestamp extract [done]
GPS_extract.Rmd
```{r}
imagedata <- getImagedata(imageURL)
```

# Image recognition API via PlantNet [done]
API-plantnet.Rmd
plantnetkey.txt
```{r}
imageURL <- 'https://photos.app.goo.gl/srRoYVB7zH3uA6qs9'
species1 <- getSpecies(key, imageURL)
```

## To-Do:
 - Image hosting option for API image access or image submission to API [done]
 - Multiple image submission for identification API

# Species data via GBIF API [incomp]
GBIF data.Rmd

# Map Image GPS [done]
GPS_map.Rmd

```{r}
map_plot
```

# Shiny time-series


