---
title: "Image extract"
output: html_document
---
> Check with system if exif is installed, if not, install exif
system("apt-get install exif")

> tools reference
http://paleolimbot.github.io/tutorial/rexiftool.html
https://exiftool.org/


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(exifr)
library(dplyr)
```

> Get from image
1) Geolocation
2) Timestamp

```{r}
getImagedata <- function(location){
  # Image can be hosted either locally or via URL
  # If image is online, downloaded locally:
filename <- ""
    if(!file.exists(location)){
    filename <- sub('.*\\/', '', location)
    download.file(url = location, filename, quiet = T)
    location <- filename                        #Convert into local URL
  }
# Else, image exif is directly returned
imagedata <- read_exif(location)

# Confirm if image has GPS properties
check_gps_properties <- names(imagedata)
if(length(grep("GPS", check_gps_properties)) == 0)
    stop("No GPS data found, please confirm image taken have GPS data through camera settings, then retake")
  # [Feature] Allow manual GPS coordinates entry via Google Maps copy and paste coordinates

# Todo:
# Write TryCatch methods to distinguish images downloaded via links (ie. Google Photos, etc [must have open access downloadable conditions])

# [Feature] Minimize column data
  # Potential select property extraction for GPS data (Need to confirm interoperability between image property names)
  # loc <- loc %>% select(FileName, 
  #                       GPSTimeStamp,  #Or DateTimeOriginal, FileAccessDate
  #                       GPSDateStamp,  #Optional
  #                       GPSDOP,        #Optional, represents `Dilution of Precision` (see table below)
  #                       GPSLatitude,
  #                       GPSLongitude
  #                       )

# Remove downloaded file
## [Feature] - save to local storage (NoSQL)
if(filename==location){
    file.remove(location)
}
return(imagedata)
}
```
Image Testing source dataset= https://www.gbif.org/dataset/7a3679ef-5582-4aaa-81f0-8c2545cafc81

```{r}
# Testing functions
## Hosted
### doesn't contain 'GPS' (will return error)
getImagedata('https://cdn.pixabay.com/photo/2020/05/09/17/04/thistle-5150476_960_720.jpg')
### Working (using GBIF source, use 'Identifier' link)
getImagedata("https://bs.plantnet.org/image/o/090f920a7c32b350e135fe1eec1b2fb4e0d81497")

## Local
getImagedata("/home/agar2/Pictures/fab3b610b796778928299f535f661984e5eebd7c.jpeg")
```

https://en.wikipedia.org/wiki/Dilution_of_precision_(navigation)
# DOP Value	Rating	Description
1	Ideal	Highest possible confidence level to be used for applications demanding the highest possible precision at all times.
1-2	Excellent	At this confidence level, positional measurements are considered accurate enough to meet all but the most sensitive applications.
2-5	Good	Represents a level that marks the minimum appropriate for making accurate decisions. Positional measurements could be used to make reliable in-route navigation suggestions to the user.
5-10	Moderate	Positional measurements could be used for calculations, but the fix quality could still be improved. A more open view of the sky is recommended.
10-20	Fair	Represents a low confidence level. Positional measurements should be discarded or used only to indicate a very rough estimate of the current location.
'>20'	Poor	At this level, measurements are inaccurate by as much as 300 meters with a 6-meter accurate device (50 DOP × 6 meters) and should be discarded.

```{r}
gpsdata <- getImagedata("https://bs.plantnet.org/image/o/090f920a7c32b350e135fe1eec1b2fb4e0d81497") 
gpsdata <- gpsdata %>% select(FileName, contains("Date"), contains("GPS"))
```


