---
title: "Image extract"
output: html_document
---
> Check with system if exif is installed, if not, install exif
system("apt-get install exif")

> tools reference
http://paleolimbot.github.io/tutorial/rexiftool.html
https://exiftool.org/


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(exifr)
library(dplyr)
```

> Get from image
1) GeoTag
  Note: Based on Exif library (https://exiftool.org/geotag.html), tags will have "GEO..." for geotags
2) Timestamp

> Geotags Listed:
GPSLatitude        GPSLongitude      GPSAltitude          GPSDateStamp
GPSLatitudeRef     GPSLongitudeRef   GPSAltitudeRef       GPSTimeStamp
GPSTrack           GPSSpeed          GPSImgDirection      GPSPitch        
GPSTrackRef        GPSSpeedRef       GPSImgDirectionRef   GPSRoll

```{r getImagedata}
getImagedata <- function(imageURL){
  # If image is online, downloaded locally:
  # TODO Allow manual naming file

  try(
    if(!file.exists(imageURL)){
        filename <- ""
        filename <- sub('.*\\/', '', imageURL)
        download.file(url = imageURL, filename, quiet = T)
        imageURL <- filename
      })
  
  imagedata <- read_exif(imageURL, tags = c("FileName",
                                            "FileSize",
                                            "ImageSize",
                                            "DateTimeOriginal",
                                            "FileAccessDate",
                                            "GPSTimeStamp",
                                            "GPSDateStamp",
                                            "GPSDOP",
                                            "GPSLatitude",
                                            "GPSLongitude"))

  # TODO [Feature] Allow manual GPS coordinates entry via Google Maps copy and paste coordinates

  # Confirm if image has GPS properties
  image.meta <- names(imagedata)
  if(length(grep("GPS", image.meta)) == 0)
      stop("No GPS data found, please confirm image taken has GPS data through camera settings, then retake")

    # TODO Write TryCatch methods to distinguish image sources (ie. Google Photos/OneDrive/Dropbox, etc)
    # Images must have open access "downloadable" conditions or have api access to log in to access
    # TODO [Feature] - save to local storage (NoSQL)

  # Remove downloaded local file
  if(filename==imageURL){
      file.remove(imageURL)
      }
  return(imagedata)
}
```
Image Testing source dataset= https://www.gbif.org/dataset/7a3679ef-5582-4aaa-81f0-8c2545cafc81

```{r}
# Testing functions
## Hosted
### doesn't contain 'GPS' (will return error)
pic.ext_1 <- 'https://cdn.pixabay.com/photo/2020/05/09/17/04/thistle-5150476_960_720.jpg'
getImagedata(pic.ext_1)
### Working (using GBIF source, use 'Identifier' link)
pic.ext_2 <- "https://bs.plantnet.org/image/o/090f920a7c32b350e135fe1eec1b2fb4e0d81497"
getImagedata(pic.ext_2)

## Local
pic.int_1 <- "/home/agar2/Pictures/fab3b610b796778928299f535f661984e5eebd7c.jpeg"
getImagedata(pic.int_1)
```

https://en.wikipedia.org/wiki/Dilution_of_precision_(navigation)
# DOP Value	Rating	Description
1	Ideal	Highest possible confidence level to be used for applications demanding the highest possible precision at all times.
1-2	Excellent	At this confidence level, positional measurements are considered accurate enough to meet all but the most sensitive applications.
2-5	Good	Represents a level that marks the minimum appropriate for making accurate decisions. Positional measurements could be used to make reliable in-route navigation suggestions to the user.
5-10	Moderate	Positional measurements could be used for calculations, but the fix quality could still be improved. A more open view of the sky is recommended.
10-20	Fair	Represents a low confidence level. Positional measurements should be discarded or used only to indicate a very rough estimate of the current location.
'>20'	Poor	At this level, measurements are inaccurate by as much as 300 meters with a 6-meter accurate device (50 DOP × 6 meters) and should be discarded.


