---
title: "API - plantnet"
output: html_document
---

devtools::install_github(repo = 'BiologicalRecordsCentre/plantnet')

```{r setup, include=FALSE}
library(plantnet)
library(dplyr)
library(httr)
library(RCurl)
```

#HTTP POST remote images
https://my.plantnet.org/account/doc
* Must use POST for local images upload, where GET for online urls
##Identification service params:

service: https://my-api.plantnet.org/v2/identify/all
api-key: api-key=2a10ugoftmL4lZtukHdV8DvDWu
image_1: images=/data/media/image_1.jpeg
image_2: images=/data/media/image_2.jpeg
organ_1: organs=flower
organ_2: organs=leaf

# Ideal flow:
Check if file is local
  If local, expand path
  POST request to Plantnet API
Else GET request to Plantnet API
Catch 400 errors
Evaluate low classification scores

```{r}
getSpecies <- function(key, location, organ) {
  
# check for local image file
  url <- paste("https://my-api.plantnet.org/v2/identify/all?api-key=", key, sep = "")
  if(RCurl::url.exists(location)){
    # Hosted image file via URL
    # query GET equivalent to cURL params
          plantnetPOST <- httr::GET(url = url, 
                              query = list(
                                images =  location,
                                organs = organ)
                           )
            }
  else({
    # local file path, in accordance with script location
      message("Sending local file to server...")
      try(
        location <- upload_file(normalizePath(location)), silent = TRUE)
        plantnetPOST <- httr::POST(url = url,
                             add_headers(`Content-Type`="multipart/form-data"),
                                  body = list(
                                    images = location,
                                    organs = organ
                                    ),
                                encode = "multipart"
                             )
    }
  )
  
# Parse response contents (Note of similar response format between local vs hosted)
   classifications_check <- httr::content(plantnetPOST)

# TODO convert to tryError Warning message
# Classification score function
  if(classifications_check$results[[1]]$score > 5) {
    species_name <- classifications_check$results[[1]]$species$scientificNameWithoutAuthor[1]
    print(paste(species_name, classifications_check$results[[1]]$score))
  }
  else {
    print("Insufficent accuracy. Not recommended to continue with current image. Please use other images")
    species_name <- classifications_check$results[[1]]$species$scientificNameWithoutAuthor[1]
    print(paste(species_name, classifications_check$results[[1]]$score))
  }

# Return value for variable storage
return(species_name)
}

```

```{r}
# Get your key from https://my.plantnet.org/
key <- as.character(read.table("../plantnetkey.txt"))   # Personal key, please do not use without permission [limited to 50 uses per day]

# Get the URL for your image
imagepath <- "https://bs.plantnet.org/image/o/090f920a7c32b350e135fe1eec1b2fb4e0d81497"
imageloc <- "../Pictures/IMG_20200729_163347.jpg"

```

```{r}
# Function test
## Saved version
test.id <- species_name <- getSpecies(key, imageloc, organ = "flower")

```


```{r rough functions}
# It's Alive!! 
# Local image API request
imageloc_upload <- upload_file(imageloc)
plantnetPOST <- httr::POST(url = paste("https://my-api.plantnet.org/v2/identify/all?api-key=", key, sep = ""),
                           add_headers(`Content-Type`="multipart/form-data"),
                                body = list(
                                  images = imageloc_upload,
                                  organs = "flower"
                                  ),
                              encode = "multipart"
                           )

# Hosted image API request
imagepath <- "https://bs.plantnet.org/image/o/090f920a7c32b350e135fe1eec1b2fb4e0d81497"
plantnetPOST <- GET(url = url, 
                    query = list(       # query in GET is equivalent to cURL params
                      images =  imagepath,
                      organs = organ)
                 )

```

Per Postman building via desktop app connection:
curl --location --request POST 'https://my-api.plantnet.org/v2/identify/all?api-key=2a10ugoftmL4lZtukHdV8DvDWu' \
--form 'images=@vfAqlnPvw/IMG_20200729_163347.jpg' \
--form 'organs=flower'

param: api-key
body: images{@file}, organs

HTTP Status Code	Reason	Response Model	Headers
400	Bad Request
401	Unauthorized
404	Species Not Found
413	Payload Too Large
414	URI Too Long
415	Unsupported Media Type
429	Too Many Requests
500	Internal Server Error